---
title: "Program Director Interviews"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Here, we present an analysis of the interviews with program directors, step by step.

load libraries
```{r}
library(GPArotation)
library(lattice)
library(nFactors)
library(psych)
library(dplyr)
library(poLCA)
library(irr)

```


read data for LCA

```{r}
lca.data <- read.table("./Binary_AllCodes_12.txt", header = TRUE)
tocluster <- lca.data[,c(-1)]
```

```{r}
wss <- (nrow(tocluster)-1)*sum(apply(tocluster,2,var))
for (i in 2:12) wss[i] <- sum(kmeans(tocluster, centers=i)$withinss)
plot(1:12, wss, type="b", xlab="Number of Clusters",
  ylab="Within groups sum of squares")
```


```{r}
lca11<- poLCA(cbind(SocietalIssue, StudentChoice, PoliticalProblem,	NotaHugeLoss,	NotMuchImpact,	Finishdegree,	GetPromotedinCareer,	LowCompletion,	LowProbabilityinJob,	WasteofInvestments,	StudenttookSomeonesplace,	N_PopularS,	NInterest,	OTransfer,	WSpeciality,	E_Workload,	FamilyI,	FinancialI,	HealthP,	Psyco_Social,	DifficulutCourse,	LearningD,	Employment,	Thesis,	Perfectionism,	Checkwithteachers,	Counseling,	ICourses,	Inform,	Tracking,	SupervisorC,	Talk,	SandCourses,	ImroveStudy_SelfM,	CurriculumDevelopmnet,	GroupDiscussions,	CantfigureSP,	DifficultConvince,	DifficultCont,	LecturersLI,	NPtakingActions,	TooLate,	WorkHours,	TMIssues,	OwnData,	UseSIS,	PositiveImp,	LiketoseeStudentD,	NagativeImp)~1, lca.data, nclass=11, nrep = 100, na.rm=FALSE, graphs=T)
```
```{r}
lca11$predclass

#the numbers below indicate the clusters of participants. For example participants Philosophy 4, Romance 4 and Pharmacy 3, have all been placed in the same cluster.
```


#codes clustering
```{r}
codes.data <- t(lca.data)

codes.data <-as.data.frame(codes.data[-1,])
colnames(codes.data)<- c("SE1","SE3","Philosophy2","Philosophy3","Philosophy4","Counselling1","Counselling2","Counselling3","Romance2","Romance3","Romance4","Pharmacy2","Pharmacy3")
```

```{r}
wss <- (nrow(codes.data)-1)*sum(apply(codes.data,2,var))
for (i in 2:37) wss[i] <- sum(kmeans(codes.data, centers=i)$withinss)
plot(1:37, wss, type="b", xlab="Number of Clusters",
  ylab="Within groups sum of squares")
```

Try the LCA for the codes clustering this time

```{r}
lca11codes<- poLCA(cbind(SE1, SE3, Philosophy2, Philosophy3, Philosophy4, Counselling1, Counselling2, Counselling3, Romance2, Romance3, Romance4, Pharmacy2, Pharmacy3)~1, codes.data, nclass=11, nrep = 100, na.rm=FALSE, graphs=T)
```

```{r}
lca11codes$predclass

#the numbers below indicate the high-order clusters of codes. The idea here is to examine whether these high-order clusters have underlying semantics.
```


```{r}
codes.data["code.clusters"] <- lca11codes$predclass
```

END



-------------mahesha-----------------------------------------
below you can transfer the code from test.R. I've tried to adapt some
# Factor Analysis for All codes

This has done for both "All codes" and "DropoutReasons"
question: what do you mean "for both"? 
-All codes means all the codes derived from the analysis (e.g: dropouts is a major concern, dropout reasons, strategies, issues)
Dropout reasosn contains the codes derived from (dropouts as a major concern and dropout reasosn ). Sicne those emhpasise the reasons for dropouts

For the factor analysis I used Freq_AllCodes and Freq_Dropout_Reasons

```{r}
#data <- read.delim(file.choose(),header = TRUE)
data <-read.delim("./Freq_AllCodes.txt", header = TRUE)
#View(data)
```

#CorrelationMatrix
question: these correlations do not take into account statistical significance, right? Yes
```{r}
raqMatrix <- cor(data[2:50])

head(round(raqMatrix, 2))
```

Based on the correlation matrix, heavily weighted (greater than 0.9) variables (negativeIM and liketo see student data) have been removed (like to see student data, do not use SIS and Negative Impression) after that PCA was calculated.


question: Not sure whats going on here? If you un-comment and re-run, it gives an error

Answer: chances are you have another package attached that also has a select function and R thinks you are calling that. Thus; I changed it as dplyr::select.  
```{r}
data <- dplyr::select(data, SocietalIssue,	StudentChoice,	PoliticalProblem,	NotaHugeLoss,	NotMuchImpact,	Finishdegree,	GetPromotedinCareer,	LowCompletion,	LowProbabilityinJob,	WasteofInvestments,	StudenttookSomeonesplace,	N_PopularS,	NInterest,	OTransfer,	WSpeciality,	E_Workload,	FamilyI,	FinancialI,	HealthP,	Psyco_Social,	DifficulutCourse,	LearningD,	Employment,	Thesis,	Perfectionism,	Checkwithteachers,	Counseling,	ICourses,	Inform,	Tracking,	SupervisorC,	Talk,	SandCourses,	ImroveStudy_SelfM,	CurriculumDevelopmnet,	GroupDiscussions,	CantfigureSP,	DifficultConvince,	DifficultCont,	LecturersLI,	NPtakingActions,	TooLate,	WorkHours,	TMIssues,	OwnData,	UseSIS,	PositiveImp)

raqMatrix <- cor(data)

head(round(raqMatrix, 2))
```


PCA to identify number of factors
```{r}
data.pca <- prcomp(data)
summary(data.pca)
plot(data.pca)
```

I used Psych package’s fa.parallel function to execute the parallel analysis. The main goal of the parallel analysis is to find out the number of factors.

```{r warning=FALSE}
parallel<-fa.parallel(data, fm='minres', fa='fa')
```

Parallel analysis suggests that the number of factors =  3  and the number of components =  NA . Further, based on the PCA also we can say, the ideal number of factors are 3. 

library(nFactors)
```{r warning=FALSE}
threefactor <- fa(data,nfactors = 3,rotate = "oblimin",fm="minres")
print(threefactor)
print(threefactor$loadings,cutoff = 0.3, sort=TRUE)
```

#--------------------Factor Analysis for Dropout Reasons and Patterns-----------------------

```{r}
dataDR <-read.delim("./Freq_Dropout_Reasons.txt", header = TRUE)
```

CorrelationMatrix
```{r}
dataDR <- cor(dataDR[2:26])

head(round(dataDR, 2))
```

PCA to identify number of factors
```{r}
dataDR.pca <- prcomp(dataDR)
summary(data.pca)
plot(data.pca)
```

Screeplot to find number of factors
```{r}
ev <- eigen(cor(dataDR)) # get eigenvalues
ap <- parallel(subject=nrow(dataDR),var=ncol(dataDR),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

based on PCA data 3 factors were executed
```{r}
threefactorDR <- fa(dataDR,nfactors = 3,rotate = "oblimin",fm="minres")
print(threefactorDR)
print(threefactorDR$loadings,cutoff = 0.3, sort=TRUE)
```

#-------------Latent Class Analysis------------------

```{r}
library(scatterplot3d)
library(MASS)
library(poLCA)
library(xlsx)
library("reshape2")
library("plyr")
library("dplyr")
library("poLCA")
library("ggplot2")
library("ggparallel")
library("igraph")
library("tidyr")
library("knitr")
```

Here as you mentioned I considered partipant statement as the unit of analysis
```{r}
dataLCA <-read.delim("./Binary_ALlCodes_Clustering.txt",header = TRUE)
```

latent class analysis for all the codes
```{r}
ds <- poLCA(cbind(SE1,	SE3,	Philosophy2,	Philosophy3,	Philosophy4,	Counselling1,	Counselling2,	Counselling3,	Romance2,	Romance3,	Romance4,	Pharmacy2,	Pharmacy3)~1, data=dataLCA, graphs = TRUE, na.rm = TRUE)
```

Select variable and define function for all codes
```{r}
mydata <- dataLCA %>% dplyr::select(SE1,	SE3,	Philosophy2,	Philosophy3,	Philosophy4,	Counselling1,	Counselling2,	Counselling3,	Romance2,	Romance3,	Romance4,	Pharmacy2,	Pharmacy3)

f<-with(mydata, cbind(SE1,	SE3,	Philosophy2,	Philosophy3,	Philosophy4,	Counselling1,	Counselling2,	Counselling3,	Romance2,	Romance3,	Romance4,	Pharmacy2,	Pharmacy3)~1)
```

models with different number of groups

```{r}
set.seed(01012)
lc1<-poLCA(f, data=mydata, nclass=1, na.rm = FALSE, nrep=30, maxiter=3000) #Loglinear independence model.
lc2<-poLCA(f, data=mydata, nclass=2, na.rm = FALSE, nrep=30, maxiter=3000)
lc3<-poLCA(f, data=mydata, nclass=3, na.rm = FALSE, nrep=30, maxiter=3000)
lc4<-poLCA(f, data=mydata, nclass=4, na.rm = FALSE, nrep=30, maxiter=3000) 
lc5<-poLCA(f, data=mydata, nclass=5, na.rm = FALSE, nrep=30, maxiter=3000)
lc6<-poLCA(f, data=mydata, nclass=6, na.rm = FALSE, nrep=30, maxiter=3000)
```

generate dataframe with fit-values

```{r}
results <- data.frame(Modell=c("Modell 1"),
                      log_likelihood=lc1$llik,
                      df = lc1$resid.df,
                      BIC=lc1$bic,
                      ABIC=  (-2*lc1$llik) + ((log((lc1$N + 2)/24)) * lc1$npar),
                      CAIC = (-2*lc1$llik) + lc1$npar * (1 + log(lc1$N)), 
                      likelihood_ratio=lc1$Gsq)
results$Modell<-as.integer(results$Modell)
results[1,1]<-c("Modell 1")
results[2,1]<-c("Modell 2")
results[3,1]<-c("Modell 3")
results[4,1]<-c("Modell 4")
results[5,1]<-c("Modell 5")
results[6,1]<-c("Modell 6")

results[2,2]<-lc2$llik
results[3,2]<-lc3$llik
results[4,2]<-lc4$llik
results[5,2]<-lc5$llik
results[6,2]<-lc6$llik

results[2,3]<-lc2$resid.df
results[3,3]<-lc3$resid.df
results[4,3]<-lc4$resid.df
results[5,3]<-lc5$resid.df
results[6,3]<-lc6$resid.df

results[2,4]<-lc2$bic
results[3,4]<-lc3$bic
results[4,4]<-lc4$bic
results[5,4]<-lc5$bic
results[6,4]<-lc6$bic

results[2,5]<-(-2*lc2$llik) + ((log((lc2$N + 2)/24)) * lc2$npar) #abic
results[3,5]<-(-2*lc3$llik) + ((log((lc3$N + 2)/24)) * lc3$npar)
results[4,5]<-(-2*lc4$llik) + ((log((lc4$N + 2)/24)) * lc4$npar)
results[5,5]<-(-2*lc5$llik) + ((log((lc5$N + 2)/24)) * lc5$npar)
results[6,5]<-(-2*lc6$llik) + ((log((lc6$N + 2)/24)) * lc6$npar)

results[2,6]<- (-2*lc2$llik) + lc2$npar * (1 + log(lc2$N)) #caic
results[3,6]<- (-2*lc3$llik) + lc3$npar * (1 + log(lc3$N))
results[4,6]<- (-2*lc4$llik) + lc4$npar * (1 + log(lc4$N))
results[5,6]<- (-2*lc5$llik) + lc5$npar * (1 + log(lc5$N))
results[6,6]<- (-2*lc6$llik) + lc6$npar * (1 + log(lc6$N))

results[2,7]<-lc2$Gsq
results[3,7]<-lc3$Gsq
results[4,7]<-lc4$Gsq
results[5,7]<-lc5$Gsq
results[6,7]<-lc6$Gsq

results
```
Calculate Enthropy
```{r}
entropy<-function (p) sum(-p*log(p))

results$R2_entropy
results[1,8]<-c("-")

error_prior<-entropy(lc2$P) # class proportions model 2
error_post<-mean(apply(lc2$posterior,1, entropy),na.rm = TRUE)
results[2,8]<-round(((error_prior-error_post) / error_prior),3)

error_prior<-entropy(lc3$P) # class proportions model 3
error_post<-mean(apply(lc3$posterior,1, entropy),na.rm = TRUE)
results[3,8]<-round(((error_prior-error_post) / error_prior),3)

error_prior<-entropy(lc4$P) # class proportions model 4
error_post<-mean(apply(lc4$posterior,1, entropy),na.rm = TRUE)
results[4,8]<-round(((error_prior-error_post) / error_prior),3)

error_prior<-entropy(lc5$P) # class proportions model 5
error_post<-mean(apply(lc5$posterior,1, entropy),na.rm = TRUE)
results[5,8]<-round(((error_prior-error_post) / error_prior),3)

error_prior<-entropy(lc6$P) # class proportions model 6
error_post<-mean(apply(lc6$posterior,1, entropy),na.rm = TRUE)
results[6,8]<-round(((error_prior-error_post) / error_prior),3)
```

combining results to a dataframe
```{r}
colnames(results)<-c("Model","log-likelihood","resid. df","BIC","aBIC","cAIC","likelihood-ratio","Entropy")
lca_results<-results

library(ztable)
ztable::ztable(lca_results)
```


#-------------------Cluster Analysis-----------------

```{r}
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms
```


```{r}
dataClus <-read.delim("./Binary_ALlCodes_Clustering.txt", header = TRUE)
```

Dissimilarity matrix
```{r}
HC <- dist(dataClus[2:14], method = "euclidean")
```

Hierarchical clustering using wards method
```{r}
hc1 <- hclust(HC, method = "ward.D2" )
```

Plot the obtained dendrogram
```{r}
plot(hc1, cex = 0.6, hang = -1)
```
Plot the obtained dendrogram with Labels
```{r}
plot(hc1, cex = 0.6, labels = dataClus$Participant, hang = -1)
```
make subgroups
```{r}
plot(hc1, labels = dataClus$Participant, cex = 0.6)
rect.hclust(hc1, k = 5, border = 2:5)
```

